```{r}
library(tidyverse)
```

```{r}
answer<-read_csv("Answers_trunc.csv")
question<-read_csv("Questions_trunc.csv")
answer
```

```{r}
question
```

```{r}
merge<-left_join(question,answer, by = "Id")
merge
```

```{r}
actual<-filter(merge,str_detect(merge$Title ,pattern = c("Who","What","How","When","Which")))
```

```{r}
notactual<-filter(merge,!str_detect(merge$Title ,pattern = c("Who","What","How","When","Which")))
notactual
```

```{r}
mean(actual$Score.x)
```

```{r}
mean(notactual$Score.x)
```


```{r}
34.83784/24.87478
```


```{r}
ggplot(data = actual)+
  geom_histogram(mapping = aes(x=Score.x))
```

```{r}
ggplot(data = notactual)+
  geom_histogram(mapping = aes(x=Score.x))
```


My research question is: Do actual questions receive a higher answering score?

Answer: Yes, actual questions(contained Who, Which, How, When, Where) received 1.4 times higher score than those are not. I used filter and str_detect functions to filter out title that contained the five key words I mentioned, and see the avg scorce of them versus those did not. From the chart, you can see not complete question had almost 10000 times of 0 scorce, which means there were not answered all all, whereas, only 350 actual questions were not answered.



