---
title: "Pink Lemonade Lab 10"
author: "Lucas Brack, Jon Guay, Harold Chang, Max Ward"
date: "March 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(stringr)
library(lubridate)
questions <- read.csv("Questions_trunc.csv")%>%select(-X)
view(questions)

answers <- read.csv("Answers_trunc.csv")%>%select(-X)
view(answers)

q_and_a <- questions%>%
  left_join(answers,by="OwnerUserId")
view(q_and_a)

```
#Team Portion

```{r,results="hide", warning=F}
q_and_a <- questions%>%
  left_join(answers, by=c("Id"="ParentId"))%>%
  select(OwnerUserId.x, Score.y, CreationDate.x, CreationDate.y)%>%
  separate(CreationDate.y, into=c("date_a", "time_a"), sep="T" )%>%separate(time_a, into=c("time_a"), sep="Z" )%>%
  separate(CreationDate.x, into=c("date_q", "time_q"), sep="T" )%>%separate(time_q, into=c("time_q"), sep="Z" )%>%
  unite(Date_q,date_q,time_q)%>%
  unite(Date_a,date_a,time_a)%>%
  mutate(Date_q = ymd_hms(Date_q))%>%
  mutate(Date_a = ymd_hms(Date_a))%>%
  mutate(Diff=(as.duration(interval(Date_q,Date_a))))%>%
  select(Score.y,Diff)%>%
  separate(Diff, into=c("Diff"), sep="s")%>%
  mutate(Diff=as.double(Diff)/(60*24))
view(q_and_a)
```

```{r,warning=F}
ggplot(data=q_and_a)+
  geom_jitter(mapping=aes(x=Diff,y=Score.y))+
  labs(title="Scores Decrease the Longer after the Question was Posted", x="Time since question was posted", y="Answer Score")+
  xlim(0,10000)+
  ylim(0,3000)
  
```

As shown in the graph above, generally the longer after a answer is given, the lower the score is. This is because less people are likely to see this answer because it is so long after the question is asked that is has probably already been answered, so it isn't useful to have more answers to the person who asked the question.

**Individual:Lucas Brack**

Do Questions with "Python" in the title score higher than those without Python in the title?
```{r,echo=FALSE, message = FALSE}
qs_no_python<-questions%>%
  filter(!str_detect(Title,pattern="python"))%>%
  select(Score)%>%
  summarize(mean(Score))
qs_no_python

qs_with_python<-questions%>%
  filter(str_detect(Title,pattern="python"))%>%
  select(Score)%>%
  summarize(mean(Score))
qs_with_python
```

Questions that say "Python" by name in the title score almost half the point compared to questions that do not mention Python by name. One possible reason for this is the questions are really simple beginners question that could easily be answered with a Google search, so there is no need to post it on the forum, so people don't up vote.

Do answers with code get better scores?
```{r, include=TRUE}
answers_no_code<-answers%>%
  filter(!str_detect(Body,pattern="<code>"))%>%
  select(Score)%>%
  summarize(mean(Score))
answers_no_code

answers_with_code<-answers%>%
  filter(str_detect(Body,pattern="<code>"))%>%
  select(Score)%>%
  summarize(mean(Score))
answers_with_code
```

As shown by the average scores, answers with actual chunks of code in them score over 4 times higher than those without code in them. This is most likely because it is more helpful to see an answer that just have it explained to you through text, so people like these answers better.


The features I choose where whether Pyton was mentioned by name in the question, and whether there was code in the answer. Having Python by name in the title lowered the score by almost half, and having code in the answer increased the score by a factor 4.

**Individual: Jon Guay**

```{r,echo=FALSE, message = FALSE, warning= FALSE}
library(tidyverse)
library(lubridate)
library(stringr)

answers <- read_csv("Answers_trunc.csv")
questions <- read_csv("Questions_trunc.csv")


answers <- answers %>%
  arrange((desc(Score))) 
  #select(-OwnerUserId)
questions <- questions %>%
  arrange(desc(Score)) 
  #select(-OwnerUserId)

combinedtable <- left_join(questions, answers, by = c("Id" = "ParentId"))
Tidydata <- arrange(combinedtable, desc(Id)) %>%
  #filter(!is.na(OwnerUserId) == TRUE) %>%
  select(-`X7.x`, `X7.y`)

test <- mutate(Tidydata, `inputlength(Questions)` = str_length(`Body.x`)) %>%
  select(-`X7.y`)



dataforplot <- mutate(test, `inputlength(Answers)` = str_length(`Body.y`))


##Do longer answers and longer questions recieve more or less upvotes?

ggplot(data = dataforplot) +
  geom_jitter(mapping = aes(x = `inputlength(Answers)`, y = `Score.y`))

ggplot(data = dataforplot) +
  geom_jitter(mapping = aes(x = `inputlength(Questions)`, y = `Score.x`))
```

Do longer answers and longer questions recieve more or less upvotes?

Answered: Simply looking at these plots we see clearly there is absolutely no correlation between the length and score of a post, however after about 10,000 character questions or answers, it tends to get no upvotes.  Likely due to the length and required reading of the post.

I choose to feature the length of the strings as my variable, as I was interested into how lengthy posts affect people's understanding of the answer and or question.  In this case, the length applied in the same fashion to both the question and answer portion of this data set.

**Individual: Harold Chang**
```{r}
library(tidyverse)
```

```{r,echo=FALSE, message = FALSE}
answer<-read_csv("Answers_trunc.csv")
question<-read_csv("Questions_trunc.csv")
answer
```

```{r}
question
```

```{r}
merge<-left_join(question,answer, by = "Id")
merge
```

```{r,echo=FALSE, message = FALSE}
actual<-filter(merge,str_detect(merge$Title ,pattern = c("Who","What","How","When","Which")))
```

```{r,echo=FALSE, message = FALSE}
notactual<-filter(merge,!str_detect(merge$Title ,pattern = c("Who","What","How","When","Which")))
notactual
```

```{r}
mean(actual$Score.x)
```

```{r}
mean(notactual$Score.x)
```


```{r}
34.83784/24.87478
```


```{r}
ggplot(data = actual)+
  geom_histogram(mapping = aes(x=Score.x))
```

```{r}
ggplot(data = notactual)+
  geom_histogram(mapping = aes(x=Score.x))
```

My research question is: Do actual questions receive a higher answering score?

Answer: Yes, actual questions(contained Who, Which, How, When, Where) received 1.4 times higher score than those are not. I used filter and str_detect functions to filter out title that contained the five key words I mentioned, and see the avg scorce of them versus those did not. From the chart, you can see not complete question had almost 10000 times of 0 scorce, which means there were not answered all all, whereas, only 350 actual questions were not answered.


**Individual: Max Ward**